---
output:
    html_document:
        keep_md: yes
---
# candysurvey

**[QUICK REFERENCE]:** The candy survey data is contained in the `candysurvey` R object of this package.

## About the data
A attempt at the cleanup of David Ng and Ben Cohen's 2015 **Halloween Candy Hierarchy** survey data

- The experiment is described at: http://boingboing.net/2015/10/23/only-you-can-determine-what-to.html
- The survey is located at: https://docs.google.com/forms/d/1XjybL7zDs479qYk9jFptDc35fjjXFyXLnTCHCMIw6pI/viewform
- The survey responses is located at: https://docs.google.com/spreadsheets/d/1REZvjqv0lj3dEYb0CsGyDXkXrjhJ4izlAEImgaufjCc/pubhtml
- The result of their survey analysis is located at: http://boingboing.net/2015/10/31/the-candy-hierarchy-2015-your.html

## Installation
You can install `candysurvey` from GitHub:

    devtools::install_github("csiu/candysurvey")

## Usage
Load the package:
```{r message=FALSE}
library(candysurvey)
library(dplyr) ## using dplyr because the data is a tbl_df object
```

```{r}
candysurvey

## Lets take a glimpse at the data
candysurvey %>% glimpse()
```

## Acknowledgement
This work -- as part of my [STAT 547M](http://stat545-ubc.github.io) coursework -- is inspired by @[jennybc/candy](https://github.com/jennybc/candy).
