---
title: "The data"
author: "csiu"
date: "November 4, 2015"
output: 
    html_document:
        keep_md: yes
---
```{r}
suppressPackageStartupMessages(library(dplyr))
```

- About the survey: http://boingboing.net/2015/10/23/only-you-can-determine-what-to.html
- Survey itself: https://docs.google.com/forms/d/1XjybL7zDs479qYk9jFptDc35fjjXFyXLnTCHCMIw6pI/viewform


```{r}
candy_survey <- read.delim("candy-survey-2015.csv", sep = ",", check.names = FALSE)

## DATA SIZE
dim(candy_survey)
```

## Candy survey questions (aka the data header)

Categories of questions on the survey related to candy:

| Category | Response | Ideal Response class |
|:--------:|:--------:|:--------------------:|
| Going trick or treating? | {yes, no} | logical |
| Age | free text | should be int |
| [the candy] | {joy, despair} | logical | 
| Other joy candy | free text | list |
| Other despair candy | free text | list |
| Comments | free text | text |

Categories of questions on the survey not-related to candy:

| Category | Response | Ideal Response class |
|:--------:|:--------:|:--------------------:|
| guess mints in hand | free text | should be int |
| Betty or Veronica? | {Betty, Veronica, ??} | factor |
| tears when | multiple choice (can select more than 1) | maybe factor | 
| the dress | {blue and black, white and gold} | factor | 
| favorite font | free text | should be factor |
| intelligent design | multiple choice + other | should be factor | 
| [separation] | {1, 2, 3+} | factor | 
| Imitation | {Flattery, Laziness, Lazily flattering someone} | factor | 
| Friday vs Sunday | {Friday, Sunday} | factor |

```{r}
candy_survey %>% 
  colnames()
```


